WordRec Experiment

### 2019-04-05 Analysis/process.Rmd
adults N 100

Sample size:
The following are the analysese done with adult pilot data.
We plan to collect data from 60 participants on Amazaon MTurk.

@@

d_adult_good <- d_adult %>%
  left_join(d_adult_excl) %>%
  filter(score >0.7) %>%
  filter(sound_dist != 'catch')

feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
```

@@

```{r}
d_child <- read_delim("data_summer_all.txt", delim = " ") %>%
  filter(type == "Test") %>%
  filter(age != 6) %>%
  filter(code != 'test',
         !is.na(code)) %>%
  filter(grepl('soph', code))%>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

feather::write_feather(d_child_good, "../saved_data/data_child.feather")

@@

Summary

sum_child <- d_child_good %>%
  group_by(sound_dist, concept_dist) %>%
  dplyr::summarise(mean = mean(iscorrect),
                   sd = sd(iscorrect),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se)

@@

Plots
```{r fig.width=3, fig.height=1.7}

@@

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ block)

>>>>

Sample size:
The following are the analysese done with adult pilot data.
We plan to collect data from 100 participants on Amazaon MTurk.

@@

d_adult_good <- d_adult %>%
  left_join(d_adult_excl) %>%
  filter(score ==1) %>%
  filter(sound_dist != 'catch')

#feather::write_feather(d_adult_good, "../saved_data/data_adult.feather")
```

@@

```{r}
d_child <- read_delim("kids_all.txt", delim = " ") %>%
  filter(type == "Test") %>%
  filter(age != 6) %>%
  filter(code != 'test',
         !is.na(code)) %>%
  filter(grepl('soph', code))%>%
  mutate(iscorrect=ifelse(answer==correct, 1, 0))

@@

#feather::write_feather(d_child_good, "../saved_data/data_child.feather")

@@

Summary children
```{r}
sum_child <- d_child_good %>%
  group_by(sound_dist, concept_dist) %>%
  dplyr::summarise(mean = mean(iscorrect),
                   sd = sd(iscorrect),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se)

@@

Plot children
```{r fig.width=5, fig.height=4}

@@

```
Summary adults

@@

  #scale_y_continuous(limits = c(0.45, 0.9))+
  theme_few()+
theme(legend.title = element_text(size=11),
      legend.text=element_text(size=11),
      axis.text = element_text(size = 11)
      ) #+ facet_grid(. ~ concept)
